---
title: "Dataset"
author: "F179412"
date: "10/15/2021"
output: pdf_document
---

Mian Mudarrib F179412
Afaq Tahir F178002
Talha Tanveer F178161


Setup of Rhdf5 Installation

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager",repo="https://cran.rstudio.com/")
BiocManager::install(version = "3.13")
BiocManager::install("rhdf5")
```

Importing Library for Future Use

```{r}
library(rhdf5)
```

Checking Structure of HDF5 File

```{r}
h5ls("dataset.hdf5")
```

This dataset contains from 2 domains of NeonScience satellite capturing temperature data of Seatle city

Each domain has divided city in to multiple booms lets take data from  domain 3 and Boom 1 for instance

```{r}
data<- h5read("dataset.hdf5","/Domain_03/OSBS/min_1/boom_1")
```

Lets display what we read at the current moment

```{r}
data
```

Lets Format the date Time Column

```{r}
new <- do.call( rbind , strsplit( as.character( data$temperature$date ) , " " ) )


```

```{r}
data$temperature<-cbind( data$temperature , NDate = new[,1] , Time = new[,2] )
```

Lets delete the old date time column 

```{r}
 data$temperature <- subset (data$temperature, select = -date)

```


Lets see the changes we have done now 

```{r}
data
```

Now lets group on date and calculate average of mean temperatures

```{r}
sub<-aggregate(data$temperature$mean, list(data$temperature$NDate), mean)
```


Now lets plot this data 

```{r}
install.packages("ggplot2",repo="https://cran.rstudio.com/")
library("ggplot2")
ggplot(data = sub, aes(Group.1, x,group = 1)) +geom_line()
```

